Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-04-04 paper/paper.tex
todo cite wang 2020 icassp
start writing on semi-supervised label propagation

Moreover, a quantitative benchmark over Medley-solos-DB has demonstrated that joint time--frequency scattering, unlike purely temporal scattering, outperforms deep convolutional networks in supervised musical instrument classification, even in a relatively large data regime with 500 to 5k samples per class \cite{anden2019tsp}.
Recently, Wang et al.~\cite{wang2019ismir} trained a classifier of playing techniques on separable (\ie{} non-joint) time--frequency scattering features \cite{anden2014tsp}, and achieved state-of-the-art results in continuous performance recordings of the Chinese bamboo flute.
Despite supplying experimental evidence that time--frequency scattering is better suited to playing technique recognition than purely temporal scattering, it remains to be seen whether these findings can scale up from a single instrument to an entire orchestra.
In addition, previous publications in time--frequency scattering, whether separable or joint, lack a human-centric evaluation, independently from any classification task.

@@

The perceptual data gathered during the perceptual experiment considers 78 \ipts, each represented by one sound recording that the subject could listen to before clustering the \ipts.
For those 78 \ipts, 31 clusterings $C_k, 0<k<31, \Card(C_k)=78$ are available, that are our reference in terms of timbre similarity.
%TODO VL update integer range for k.
% Describe every k as an equivalency class
\ja{What is $C_k$ here?
Also, should it be $0 < k \le 31$?
Might be more natural to say that $k = 1, 2, \ldots, 31$, in that case.}%
If \ipt $i$ and \ipt $j$ are clustered together by subject $k$, then $C_k(i)=C_k(j)$.
In essence, an effective ranking system should retrieve sounds that belong to \ipts that are clustered together in each of the 31 clusterings.
Depending on the preferences of subjects, there may be competition between clusterings that should be mitigated when appreciating quantitatively the ranking performance.

>>>>

Moreover, a quantitative benchmark over Medley-solos-DB has demonstrated that joint time--frequency scattering, unlike purely temporal scattering, outperforms deep convolutional networks in supervised musical instrument classification, even in a relatively large data regime with 500 to 5k samples per class \cite{anden2019tsp}.
Recently, Wang et al.~\cite{wang2019ismir} trained a classifier of playing techniques on separable (\ie{} non-joint) time--frequency scattering features \cite{anden2014tsp}, and achieved state-of-the-art results in continuous performance recordings of the Chinese bamboo flute. % TODO cite wang 2020 icassp
Despite supplying experimental evidence that time--frequency scattering is better suited to playing technique recognition than purely temporal scattering, it remains to be seen whether these findings can scale up from a single instrument to an entire orchestra.
In addition, previous publications in time--frequency scattering, whether separable or joint, lack a human-centric evaluation, independently from any classification task.

@@

In music information retrieval, the core motivation behind timbre similarity modeling lies in the prospect of navigating an online corpus of digital music.
The typical size of such a corpus ranges between $N\sim10^3$ and $N\sim10^7$, depending on the use case.
As of today, the two largest databases of isolated musical notes with extended playing techniques are FullSOL and conTimbre, with $N\sim1.2\cdot10^5$ and $N\sim8.7\cdot10^4$ samples respectively.% TODO cite FullSOL and conTimbre
In comparison, the instrument--mute--technique (IMT) triplets in the present study on human subjects amount to merely $N=78$ samples, \ie{} three orders of magnitude less than conTimbre.
%even though there is expert pre-screening, etc.
% does not reflect the typical scale at which these systems are deployed.

%The perceptual data gathered during the perceptual experiment considers 78 \ipts, each represented by one sound recording that the subject could listen to before clustering the \ipts.
%For those 78 \ipts, 31 clusterings $C_k, 0<k<31, \Card(C_k)=78$ are available, that are our reference in terms of timbre similarity.
%TODO VL update integer range for k.
% Describe every k as an equivalency class
%\ja{What is $C_k$ here?
%Also, should it be $0 < k \le 31$?
%Might be more natural to say that $k = 1, 2, \ldots, 31$, in that case.}%
%If \ipt $i$ and \ipt $j$ are clustered together by subject $k$, then $C_k(i)=C_k(j)$.
%In essence, an effective ranking system should retrieve sounds that belong to \ipts that are clustered together in each of the 31 clusterings.
%Depending on the preferences of subjects, there may be competition between clusterings that should be mitigated when appreciating quantitatively the ranking performance.
